Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-10 WSSSPE1_report/WSSSPE1_summary_report.tex
Added a paragraph to address optional improvement
Added an additional paragraph discussing long term projects that
were discussed in the workshop, and explore what that means. Tried
to keep to projects where it was obvvious they have been active for
over a decade - sorry if I missed any!

>>>>

It should be noted that several articles that discussed long-term projects, that
could be said to have reached a sustainable period. The Visualization Toolkit
(VTK) was described~\cite{Hanwell_WSSSPE}, being one of the oldest projects
serving as a basis for several other tools such as ParaView~\cite{Hanwell_WSSSPE}, VisIt~\cite{Ahern_WSSSPE}, and VisTrails~\cite{Koop_WSSSPE}. Other examples of
long-term, sustainable projects included MVAPICH~\cite{Panda_WSSSPE} which began
development in 2000, R/qtl~\cite{Broman_WSSSPE} which also began development
in 2000, and DUNE~\cite{Blatt_WSSSPE} which is also over a decade old. In
addition to how long a project has been active other metrics are important,
such as number of developers, number of institutions, and whether there are
active developers acting as advocates for the continued viability of a project
beyond individual projects and/or institutions.
